---
title: "Catch em All"
author: "mntzj"
date: '2021-09-18'
excerpt: ''
layout: single
series: null
slug: []
subtitle: ''
tags:
- pokemon
- api
- json
- purrr
categories: []
---

In this post, we are going to go into the pokemon world and try to catch some
through the API [pokeapi.co](https://pokeapi.co/). A fun way to get familiar with 
working with APIs and handling JSON response with nested lists into tidy and nice rectangles of data.
![Hehe](https://lh3.googleusercontent.com/proxy/J6QEl0JbwBX1zPstq2W3OWk7iVdRGZHXWcfdboF2oNdpHtxEIkrdTwUbyvJneyzmppyTCK5hAIGUWKyeQAeBKW0I9i0EJTVInuca0_O9jPocZEVqJ5Cywk59bDhjU-d42UTxL7IP7UbPi7Qb__T322Uh96bOpGwDYfI)

_note that in this example no authentication is required to access this API, and all resources are fully open and available_ ..

```{r load em all}
library(httr, quietly = TRUE, warn.conflicts = FALSE)
library(jsonlite, quietly = TRUE, warn.conflicts = FALSE)
library(tidyverse, quietly = TRUE, warn.conflicts = FALSE)
```

```{r api}
poke_base <- "https://pokeapi.co/api/v2/"
pokemon_endpoint <- "pokemon"
records_limit <- "/?limit=200"
call <- paste0(poke_base,pokemon_endpoint,records_limit)
```

```{r request}
catch_em_all <- httr::GET(url = call)
catch_em_all$status_code
response_content <- httr::content(catch_em_all, as = "text")
```

```{r serialize}
pokemons_json <- jsonlite::fromJSON(response_content, flatten = TRUE)
pokemons_tibble <- as_tibble(pokemons_json$results)
```

```{r first catch}
catch_pokemon <- function(pokemon, poketable=pokemons_tibble)
{
  .poke_url = poketable[match(pokemon, poketable$name), 2] %>% pull()
  .catch = httr::GET(url = .poke_url)
  .content = httr::content(.catch, as = "text")
  return(jsonlite::fromJSON(.content, flatten = TRUE))
}

catch_pokemon("charmander") %>% str(max.level = 1)
```

```{r team rocket hold up}
pokenets <- map(pokemons_tibble$name, catch_pokemon)
names(pokenets) <- pokemons_tibble$name
#These are our pokemons
```

```{r tidy data, message = FALSE, echo = FALSE}
str(pokenets, max.level = 1)


stats_names <- pluck(pokenets,1,"stats","stat.name")

extract_basestats <- function(pokerow) {
  pluck(pokenets,pokerow,"stats","base_stat") %>%
    as.double() %>%
    set_names(nm = stats_names)
}

extract_type <- function(pokerow) {
  pluck(pokenets, pokerow, "types", "type.name") %>%
    paste() 
  }

pokenets_tbl <- tibble(pokenets) %>%
  unnest_wider(pokenets) %>%
  select(name, height, weight) %>%
  mutate(pokedata = map(row_number(),extract_basestats)) %>%
  unnest_wider(pokedata) %>%
  mutate(poketype = map(row_number(),extract_type)) %>%
  unnest_wider(poketype)

```
```{r}
library(corrr)

pokenets_tbl %>%
  select(height:speed) %>%
  correlate() %>%
  rearrange() %>%
  shave() %>%
  rplot(shape = 15, colours = c("darkorange", "white", "darkcyan"))
```

#todo :  perform PCA and or Lin Reg



